Figures

### 2019-07-29 figures/02_hierarchical_demo.Rmd
towards consistent cartography

```{r 02_hierarchical_demo, echo=FALSE, message=TRUE, eval=TRUE}
# setwd("figures")
ids <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

lg <- lagosne_load("1.087.1")

ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
                summarize(
                  group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
                           lagoslakeid), 
                  tp = median(tp, na.rm = TRUE), 
                  chla = median(chla, na.rm = TRUE)), 
                by = "lagoslakeid") %>%
  tidyr::drop_na()

@@

gg_lines <- ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme_cowplot() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct)", # , NLCD 2011
         y = "TP (ug/L)")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 150)) + 
    scale_color_manual(values = rep("black", 26))

gg_hu4 <- ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat, alpha = n)) +
    coord_sf(datum = NA) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
    theme_minimal() +
    theme(legend.position = 0,
          axis.title = element_blank(),
          legend.title = element_blank()) +
    scale_fill_manual(values = rep("black", 5)) +
  ggtitle("# of lakes per region")

>>>>

```{r 02_hierarchical_demo, echo=FALSE, message=TRUE, eval=TRUE}
# setwd("figures")
cl            <- cart_layers()
ep            <- cl$ep
states        <- cl$states
study_bbox    <- cl$study_bbox

dt            <- readRDS("../data/dt.rds")

ids <- dt %>%
  group_by(hu4_zoneid) %>% 
  tally()

@@

lg <- lagosne_load("1.087.1")
ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
                summarize(
                  group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
                           lagoslakeid), 
                  tp = median(tp, na.rm = TRUE), 
                  chla = median(chla, na.rm = TRUE)), 
                by = "lagoslakeid") %>%
  tidyr::drop_na()

@@

gg_lines <- ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # scale_y_log10() + scale_x_log10() +
    theme_cowplot() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct)", # , NLCD 2011
         y = "TP (ug/L)")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 150)) + 
    scale_color_manual(values = rep("#a50f15", 26))

gg_hu4 <- 
  ggplot() +
    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
              color = "black", fill = "#1D9DCF") +
    geom_sf(data = states, fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = hu4, aes(fill = n_cat), color = "black", size = 0.4) +
  scale_fill_manual(values = c("#fee5d9", "#fcae91", "#fb6a4a", "#de2d26", "#a50f15")) +
    coord_sf(datum = NA) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
    theme_minimal() +
    theme(legend.position = 0,
          axis.title = element_blank(),
          legend.title = element_blank()) +
  ggtitle("# of lakes per region")

### 2019-07-29 figures/07_model-selection.Rmd
figure cleanup
towards consistent cartography

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}

# map significant random effects hu4s
gg_hu4 <- ggplot() +
    geom_sf(data = hu4) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    coord_sf(datum = NA) +
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
    guides(guide_legend(nrow = 2))

@@

  model$res_test <- abs(
    median(model$res_med$.residual_median, na.rm = TRUE)) < threshold
  model
}
lg <- lagosne_load()
fit <- get_residuals(fit)

>>>>

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
cl            <- cart_layers()
states        <- cl$states
study_bbox    <- cl$study_bbox

# map significant random effects hu4s
gg_hu4 <- 
  ggplot() +
    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
              color = "black", fill = "#1D9DCF") +
    geom_sf(data = states, fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = hu4, fill = "white", color = "black", size = 0.4) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    coord_sf(datum = NA) +
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
    guides(guide_legend(nrow = 2))

@@

  model$res_test <- abs(
    median(model$res_med$.residual_median, na.rm = TRUE)) < threshold
  model
}
lg <- lagosne_load("1.087.1")
fit <- get_residuals(fit)
